Revisiting the Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation using complex Empirical Orthogonal Functions

### 2021-08-12 analysis/paper/shceof.Rmd
Agerga ticks

guide_colorsteps_bottom <- function(width = 15, height = 0.5, even.steps = FALSE, 
                                    title.position = "top", show.limits = TRUE,
                                    ...) {
  guide_colorsteps(show.limits = show.limits, even.steps = even.steps,
                   title.position = title.position, title.hjust = 0.5,
                   barheight = height,
                   barwidth = width, frame.colour = "black", ...)
}

@@

    geom_contour_fill(data = sst_gdata,
                      aes(z = estimate, fill = ..level..), 
                      breaks = breaks_sst) +
    geom_contour_pval(data = sst_gdata, aes(z = p_val)) +
    scale_fill_divergent_discretised("SST (K)", 
                                     labels = one_less,
                                     guide = guide_colorsteps_bottom(width = 15,
                                                                     show.limits = FALSE,
                                                                     order = 1)) +
    scale_x_longitude() +
    scale_y_latitude() +
    scale_mag(guide = "none") +
    facet_grid(term ~ var) +
    # coord_quickmap(ylim = c(NA, 10)) +
    coord_sf(ylim = c(-90, 0),
             crs = "+proj=longlat +pm=180 +over",
             default_crs = "+proj=longlat +over") + 
    theme(legend.box = "horizontal", legend.text = element_text(size = rel(0.7))) +
    tag_facets("cr", position = "bl") 
}
```

>>>>

guide_colorsteps <- function (even.steps = TRUE, show.limits = NULL, ticks = FALSE, 
  ...) {
  guide <- guide_colourbar(raster = FALSE, ticks = ticks, 
    nbin = 300, ...)
  guide$even.steps <- even.steps
  guide$show.limits <- show.limits
  class(guide) <- c("colorsteps", class(guide))
  guide
}
guide_colorsteps_bottom <- function(width = 15, height = 0.5, even.steps = FALSE, 
                                    title.position = "top", show.limits = TRUE, ticks = TRUE,
                                    ...) {
  guide_colorsteps(show.limits = show.limits, even.steps = even.steps,
                   title.position = title.position, title.hjust = 0.5,
                   barheight = height, ticks = ticks,
                   ticks.colour = "black",
                   barwidth = width, frame.colour = "black", ...)
}

@@

    geom_contour_fill(data = sst_gdata,
                      aes(z = estimate, fill = ..level..), 
                      breaks = breaks_sst) +
    geom_contour_pval(data = sst_gdata, aes(z = p_val)) +
    scale_fill_divergent_discretised("SST (K)", 
                                     labels = one_less,
                                     guide = guide_colorsteps_bottom(width = 15,
                                                                     show.limits = FALSE, ticks = TRUE,
                                                                     order = 1)) +
    scale_x_longitude() +
    scale_y_latitude() +
    scale_mag(guide = "none") +
    facet_grid(term ~ var) +
    # coord_quickmap(ylim = c(NA, 10)) +
    coord_sf(ylim = c(-90, 0),
             crs = "+proj=longlat +pm=180 +over",
             default_crs = "+proj=longlat +over") + 
    theme(legend.box = "horizontal", legend.text = element_text(size = rel(0.7))) +
    tag_facets("cr", position = "bl") 
}
